Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research

### 2023-12-03 data/sleep and HBP.Rmd
update

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
subtitle: "By Yingjie Su and published in Nature Scientific Reports"
date: "  `r format(Sys.time(), '%d %B, %Y')` "
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{fvextra}
- \usepackage{float}
- \usepackage{wrapfig}
- \usepackage{amsmath}
- \usepackage{threeparttable} %used to fix table with notes
- \usepackage{float}
- \usepackage{graphicx}
- \usepackage{microtype}
- \usepackage{setspace}
- \usepackage[font=singlespacing]{caption} #can change font here for captions here!!
- \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines, commandchars=\\\{\}}
- \singlespacing
fontsize: 10pt
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    toc_depth: 4
    number_sections: false
    keep_md: false
link-citations: yes
colorlinks: yes
linkcolor: blue
urlcolor: blue
#bibliography: refs.bib
bibliostyle: apalike
editor_options: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Preparing the NHANES Data for the Replication of: Association between sleep duration on workdays and blood pressure in non‑overweight/obese population in NHANES: a public database research"
subtitle: "By Yingjie Su and published in Nature Scientific Reports"
author: "Amos Okutse, Brown University"
date: "  `r format(Sys.time(), '%d %B, %Y')` "
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{fvextra}
- \usepackage{float}
- \usepackage{wrapfig}
- \usepackage{amsmath}
- \usepackage{threeparttable} %used to fix table with notes
- \usepackage{float}
- \usepackage{graphicx}
- \usepackage{microtype}
- \usepackage{setspace}
- \usepackage[font=singlespacing]{caption} #can change font here for captions here!!
- \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines, commandchars=\\\{\}}
- \singlespacing
fontsize: 10pt
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: false
    toc_depth: 4
    number_sections: false
    keep_md: false
link-citations: yes
colorlinks: yes
linkcolor: blue
urlcolor: blue
#bibliography: refs.bib
bibliostyle: apalike
editor_options: 
  markdown: 
    wrap: 72
---
